---
title: "Simulation Study for `feature.selector()`"
author:
- Daniel Anadria
- Ola Dacko
output:
  html_document:
    df_print: paged
    css: Simulation_Study.css
---

```{r, echo = F, warning = F, message = F}
library(tidyverse)
library(knitr)
library(kableExtra)
```



This is a  simulation study exploring the benefits of using filter, wrapper and hybrid feature selection methods for multiple imputation. The best resulting algorithms will be implemented to R `mice` package in form of a new function called `feature.selector()`.

The following algorithms are tested:


```{r, echo = F, results = 'asis'}
Method <- c("Filter", "Wrapper", "Hybrid")
Algorithm <- c("ReliefF; Miminal Redundancy Maximal Relevance (mRMR)", 
               "Genetic Algorithm (GA); Particle Swarm Optimization (PSO); Ant Colony Optimization (ACO)",
               "ReliefF and mRMR with GA PSO, ACO")

kableExtra::kable(tibble(Method, Algorithm), booktabs = T) %>%
  kable_styling(position = "center")

```


The simulation study has the following design:

```{r, echo = F}
Outcome <- c("Binary", "Multiclass", "Continuous")
Noise <- c(rep("Low, Medium, High",3))


kableExtra::kable(tibble(Outcome, Noise), booktabs = T) %>%
  kable_styling(position = "center")

```


# Introduce Missingness to a Dataset

```{r load-data}
# Boston dataset from MASS
data <- MASS::Boston
```

```{r create-missingness}
# for loop to create missing data in any dataset (50% missingness)
set.seed(42)

miss <- list()

for (variable in 1:ncol(data)) {
  miss[[variable]] <- sample(nrow(data), 0.5*nrow(data))
  data[miss[[variable]], variable] <- NA
}

# check if it worked
paste("The missing value proportion:", 
      sum(is.na(data$lstat)) / nrow(data)) # prop of missing values
```
