---
title: "Simulation May - Onwards"
output:
  html_document:
    df_print: paged
---

# Predictor Selection Function 

* create a function that mimics quickpred with a filter/wrapper/hybrid approach to feature selection


# Simulate Data

* generate a single mvrnorm distribution with N = 10K and p = 10 which consists of:
  - Set 1: 5 predictors have rho of .5
  - Set 2: 5 predictors have rho of 0


```{r}
library(MASS) # for mvrnorm

N <- 10000  # number of observations
p <- 5     # number of predictors

# Set 1: Correlated predictors (r = 0.5)
cor_matrix1 <- matrix(0.5, nrow = p, ncol = p) # create correlation matrix
diag(cor_matrix1) <- 1  # set diagonal elements to 1

# Set 2: Uncorrelated predictors (r = 0)
cor_matrix2 <- matrix(0, nrow = p, ncol = p) # create correlation matrix
diag(cor_matrix2) <- 1  # Set diagonal elements to 1

# Generate multivariate normal data
set.seed(7)
set1 <- mvrnorm(N, rep(0, p), cor_matrix1) # N, mean vector, covariance matrix
set2 <- mvrnorm(N, rep(0, p), cor_matrix2) # N, mean vector, covariance matrix

# Combine both sets
data <- cbind(set1, set2)

```

## Inspect the Simulated Data

```{r}
# View the first few rows of the generated data
head(data)
```




```{r}
round(cor(set1),1) # correlate features within set 1
```

```{r}
round(cor(set2),0)
```

```{r}
round(cor(data),1)
```

```{r}
dim(data)
```

```{r}
mvrnorm(N, rep(0, p), cor_matrix1)
```


# Induce Missingness 

* Make the simulated data incomplete 50% MCAR
* Do this nsim times

```{r}

```
